\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
summary of DMN with reference

It has been hypothesized that the adaptive role of memory retrieval is to facilitate 
construction of episodes to prepare for immediate and distant future scenarios.
So the DMN is involved in remembering the past, imagining the future, and story
comprehension. \cite{defaultnetworkadaptive}

\todo{Summarize DMN? Maybe introduce why it's relevant to meditation?}

@@

>>>>

It has been hypothesized that the adaptive role of memory retrieval is to facilitate 
construction of episodes to prepare for immediate and distant future scenarios. \cite{defaultnetworkadaptive}
The DMN is therefore involved in remembering the past, imagining the future, and story
comprehension. \cite{defaultnetworkadaptive}

\todo{Summarize DMN? Maybe introduce why it's relevant to meditation?}
Therefore the DMN that plays a role in constructing a sense of self, in memory, 
in thinking about other also lends itself to excessive rumination and anxiety. \citr{dmndepression} 
When I sit down to meditate and my thoughts wander away (and how they wander!),
it is the DMN that is being activated.

@@

\bibitem{dmndepression}
  J. Paul Hamilton, Madison Farmer, Phoebe Fogelman, and Ian H. Gotlib.
  \textit{Depressive Rumination, the Default-Mode Network, 
   and the Dark Matter of Clinical Neuroscience}
   Biol Psychiatry. 2015 Aug 15; 78(4): 224–230. doi: 10.1016/j.biopsych.2015.02.020
